Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-18 ICLR25/formula.tex
update formula.tex

One of the key formula is to choose some nodes and set the corresponding variables to be binary variable in the MILP model. We will say that we open those nodes. In our algorithm, we will open nodes at most 3 layer3 before the target layer. So the formula will consists of three parts.

>>>>

The formula is to choose some nodes and set the corresponding variables to be binary variable in the MILP model. For convenience, we will say that we open those nodes, or nodes are opened to describe that those nodes' variable are set to be binary. In our algorithm, we will open nodes at most 3 layer3 before the target layer. So the formula will consists of three parts.
